Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-26 paper/galsize_paper.tex
Minor edits to section 5

In the previous section, comparing model predictions to the observed size dependence of galaxy clustering produced two intriguing results. First, the model that assumes $\rhalf\propto\rvir$ predicts a dependence of both the amplitude and shape of  size-dependent galaxy correlation functions remarkably well, especially considering that the model nominally has only one free parameter: the normalization of the linear $\rhalf-\rvir$ relation. At the same time, small galaxies cluster more strongly relative to large, which seems at odds with naive expectations that, within such a model, larger sizes correspond to larger halo masses, $\rvir\propto\mvir^{1/3}$, and so larger sizes should be clustered more strongly. Second, the strong dependence of galaxy clustering on size weakens to almost no dependence for samples of red and blue galaxies selected by color within a given stellar mass range.
Below we propose a simple and unified explanation of all these results within the $\rvir$-based size model in \S\ref{subsec:censat_sizes}, and discuss the broader implications of our interpretation in \S\ref{subsec:broader_implications}.

>>>>

In the previous section, comparing model predictions to the observed size dependence of galaxy clustering produced two intriguing results. First, the model that assumes $\rhalf\propto\rvir$ predicts a dependence of both the amplitude and shape of  size-dependent galaxy correlation functions remarkably well, especially considering that the model nominally has only one free parameter: the normalization of the linear $\rhalf-\rvir$ relation. At the same time, small galaxies cluster more strongly relative to large, which seems at odds with intuitive expectations that, within such a model, larger sizes correspond to larger halo masses, $\rvir\propto\mvir^{1/3}$; thus  naively, galaxies with larger sizes should be more strongly clustered, not less. Second, the strong dependence of galaxy clustering on size weakens to almost no dependence for samples of red and blue galaxies selected by color within a given stellar mass range.
Below we propose a simple and unified explanation of all these results within the $\rvir$-based size model in \S\ref{subsec:censat_sizes}, and discuss the broader implications of our interpretation in \S\ref{subsec:broader_implications}.
